A thesis draft

### 2018-11-28 res/sections/20-VNFImplementaton.tex
Fix typos

All the SFC-related components have been developed with the idea of being
containerized. This is a foundamental concept, because in this way all the
components have the possibility to run inside Kubernetes, granting them the
scalability and persistence benefits. On top of that, the use of
\verb!Deployment! granted the possibility to perform easy an update of already
existing components.

@@

Another important aspect to keep in consideration is how communications inside
the chain are performed. The packet arriving in the ingress needs to be
perserved, so that VNFs can perform packet elaboration. In order to otain this,
packet encapsulation has been used. IP in IP encapsulation allow to preserve the
original packet, making the incoming packet the payload of a new one.

@@

Finally, we were able to create bidirectional chains, resistent to faults and
degradations that saddisfty the defined requirements.

>>>>

All the SFC-related components have been developed with the idea of being
containerized. This is a fundamental concept, because in this way all the
components have the possibility to run inside Kubernetes, granting them the
scalability and persistence benefits. On top of that, the use of
\verb!Deployment! granted the possibility to perform easy an update of already
existing components.

@@

Another important aspect to keep in consideration is how communications inside
the chain are performed. The packet arriving in the ingress needs to be
preserved, so that VNFs can perform packet elaboration. In order to obtain this,
packet encapsulation has been used. IP in IP encapsulation allow to preserve the
original packet, making the incoming packet the payload of a new one.

@@

Finally, we were able to create bidirectional chains, resistant to faults and
degradation that satisfy the defined requirements.
